Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-05-13 Latex/sections/results.tex
Added todo for fabi; added clustering info to cylon; slightly resized cylon image

Figure~\ref{fig:cylon-corrected} shows the results obtained before  and after employing the plane base registration on the dataset acquired by the floating sphere.
\begin{figure*}
	\centering
	\includegraphics[width=0.49\textwidth]{./images/cylon_uncorr_corner}\hfill
	\includegraphics[width=0.49\textwidth]{./images/cylon_corr_corner}\\
	\includegraphics[width=0.49\textwidth]{./images/cylon_uncorr_top}\hfill
	\includegraphics[width=0.49\textwidth]{./images/cylon_corr_top}
	\caption{The point cloud acquired by the floating sphere before (left) and after (right) applying the plane based registration. View from the interior that shows the used planes (top) and a birds-eye view (bottom). An animation of the registration process is given at \href{https://youtu.be/8XdIUN_9VpY}{here}.}
	\label{fig:cylon-corrected}
\end{figure*}
After the registration the walls of the room are significantly more prominent in the point-cloud. 
In particular the noise in the top left corner of the top view (cf. figure~\ref{fig:cylon-corrected}) has been visibly reduced.
Further, the deviation of points around the walls is notably smaller as the points are moved on the plane.

>>>>

Figure~\ref{fig:cylon-corrected} shows the results obtained before and after employing the plane base registration on the dataset acquired by the floating sphere.
We combine ten scans into one meta-scan, which is then globally registered.
This does not only speed up convergence due to the proportional effect on the error function, but also decreases the risk of transforming the scan in a sensless way.
Transformations like these happen when points that have been labled incorrectly have a huge effect on the error gradient, which is especially the case when considering only a few points.

\begin{figure*}
	\centering
	\includegraphics[width=0.49\textwidth]{./images/cylon_uncorr_corner}\hfill
	\includegraphics[width=0.49\textwidth]{./images/cylon_corr_corner}\\
	\includegraphics[width=0.49\textwidth]{./images/cylon_uncorr_top}\hfill
	\includegraphics[width=0.49\textwidth]{./images/cylon_corr_top}
	\caption{The point cloud acquired by the floating sphere before (left) and after (right) applying the plane based registration. View from the interior that shows the used planes (top) and a birds-eye view (bottom). An animation of the registration process is given at \href{https://youtu.be/8XdIUN_9VpY}{here}.}
	\label{fig:cylon-corrected}
\end{figure*}
After the registration the walls of the room are significantly more prominent in the point-cloud. 
In particular the noise in the top left corner of the top view (cf. figure~\ref{fig:cylon-corrected}) has been visibly reduced.
Further, the deviation of points around the walls is notably smaller as the points are moved on the plane.
